Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2016-12-09 Ben_Manuscripts/Paper1/Manuscript.tex
Starting writing up methods/ system setup section

	HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16. All molecular dynamics simulations were run using Gromacs version 5.1.2.

	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
	\begin{itemize}
		\item Initially parameterized monomer gives unfavorable structure
		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
		\item Result not global minimum but close enough for structure building
		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
		%BJC: Openeye software to get the best charge for multiple configurations.
		\item New configurations used for reparamaterization, BUT most likely will just use one set of charges for one configuration since I've done 90 percent of simulations based on one parameterization. In the future, I will have a single set of parameters.
	\end{itemize}

	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length. 
	\begin{itemize}
		\item Work done that shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
		\item Attempts with Colh system not fruitful  
		\begin{itemize}
			\item Packed monomers into box
			\item Simulated for ~100 ns with no real progress shown towards self assembly
		\end{itemize}  
		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
		\item Code has adjustable parameters: Pore-to-Pore distance, pore radius, number of monomer layers (justification for parameters chosen in following paragraphs)
		\item This is the thermotropic phase, information used depends on thermotropic experimental data
	\end{itemize}

        The validity of our model can be tested based on its agreement with experimental structural and material property data
        \begin{itemize}
                \item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
                \item Tougher with a large system for which no force fields have been specifically developed
	\end{itemize}

	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
	\begin{itemize}
		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
		\item Small number of layers create micellar structure
		\item Beyond 20 layers is unnecessary to get expected configuration
		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
	\end{itemize}

	\noindent The remaining parameters were chosen based on experimental data. 
	\begin{itemize}
		\item SAXS to get an idea of Pore-to-Pore
		\begin{itemize}
			\item multiple starting pore to pore distances tested (3.0, 3.5, 4.0, 4.5 nm)
			\item 4.0 nm and 4.5 nm converged to similar dimensions, 4.5 nm was most reliable
		\end{itemize}
		\item TEM images and rejection give a pore size estimate
	\end{itemize}

	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
	\begin{itemize}
		\item Monitored 'hexagonality' - i.e. how the distance between pores compares to an ideal hexagon
		\item Varied initial pore-to-pore distance and ran very long simulations - typically > 200 ns
	\end{itemize}

>>>>

	Col\subscript{h} phase forming monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16. All molecular dynamics simulations were run using Gromacs version 5.1.2. An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer. The structure was cooled from 1000 to 50 K over the course of 10 nanoseconds, resulting in a structure suitable for packing into a simulation box. Multiple configurations were saved from the annealing trajectory to be used in parallel in order to prove independence of starting configuration. A new set of parameters was generated from the annealed structure and used for all configurations tested.

	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length. Past work has shown the ability of other liquid crystals to form into various phases including the hexagonal phase using coarse grain models in c.a. 1000 ns. While 1000 ns would be expensive with an atomistic model, it is not an unreasonable amount of time and prompted an attempt at a self assembly. 480 monomers were packed into a cubic box using Packmol software, with box dimensions chosen based on approximate density of the col\subscript{h} phase. The box was made slightly larger than this to help with Packmol convergence and to give the monomers room to reorient themselves during equilibration. NPT simulations were carried out for 100 ns. In that time, no visible progress was made towards self assembly so simulations were stopped. Even if self assembly happened eventually, it is not a sustainable way to set up the system due to computational cost.

	A script was written to place monomers into a configuration close to the expected equilibrium structure in order to minimize equilibration time. The code makes copies of monomers and rotates them to form disks with a hydrophilic center. The disks are stacked on top of each other to form pores and the pores are duplicated to form a unit cell. The code has adjustable build parameters which should be chosen based on experimental data when possible. Parameters include number of monomers in a disk, the number of disks stacked on top of each in each pore, the distance between the stacked disks, the distance between pores, and the pore radius as defined by the distance between a chosen atom in the monomer and the axis around which the monomers are rotated to form the disks. In all simulations, an initial configuration consisting of four pores was packed into a monoclinic unit cell. The monoclinic unit cell with an angle between the x and y vectors of 60 degrees, is the smallest unit cell which will give hexagonal symmetry with periodic boundaries turned on.

        The validity of our model can be tested based on its agreement with experimental structural and material property data. Our simulations should mimic the real system as best as possible within the limits imposed by choice of force field. This system is particularly difficult since there has not been a forcefield developed for it and the system has not been studied in the past. Therefor, parameters were chosen carefully based on the ability to reproducibly create acceptably accurate structures.

	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. Using too few layers resulted in system which moved towards a micelle-like configuration. The number of layers was progressively increased until straight pores in a hexagonal configuration proved stable. Anything beyond 20 layers provided no extra information only contributing computational expense.

	The spacing between layers has a significant impact on the system dimensions. It should be between 4 A and 7 A, with a recommended value of 5 A. A spacing below 4 angstroms risks large repulsions between layers during the first steps of simulation giving unpredictable results. A spacing greater than 7 A has consistently given structural dimensions that are too small. It is hypothesized that it is due to monomer layers slipping between each during the first picoseconds of simulation. The system gets locked into a metastable state from which there is no recovery. A spacing of 5 A allows a more gentle relaxation and subsequent relaxation into a experimentally consistent configuration.

	Experimental small angle X-ray scattering results were used to inform our choice of an initial pore to pore distance. The peak corresponding to the d100 plane was used to estimate a distance between pores of 4.12 nm. The sensitivity of the system to the starting pore-to-pore distance was tested by simulating initial configurations with starting pore-to-pore distances of 3.0, 3.5, 4.0 and 4.5 nm. Using 3.0 and 3.5 nm resulted in a structure whose dimensions were too small. The significant overlap between pores at these initial conditions likely locked the pores together with no hope of separation without energy input. Starting pore-to-pore distances of 4.0 and 4.5 nm both converged to expected distances.   
	\begin{itemize}
		\item SAXS to get an idea of Pore-to-Pore
		\begin{itemize}
			\item multiple starting pore to pore distances tested (3.0, 3.5, 4.0, 4.5 nm)
			\item 4.0 nm and 4.5 nm converged to similar dimensions, 4.5 nm was most reliable
		\end{itemize}
		\item TEM images and rejection give a pore size estimate
	\end{itemize}

	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
	\begin{itemize}
		\item semi-isotropic
		\item Monitored 'hexagonality' - i.e. how the distance between pores compares to an ideal hexagon
		\item Varied initial pore-to-pore distance and ran very long simulations - typically > 200 ns
	\end{itemize}
